### 2018-03-22 reports/thesis/chapters/5_inference.tex
Adjusted multiple hypothesis section.

In this section, the single hypothesis test will be extended and the multiple hypothesis testing \citep{shaffer1995multiple} shall be reviewed.

@@

The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate. The FDR is the proportion of false positives out of all positive results, that is
\begin{equation}
    \expectation[\text{FDR}] = \expectation\left[
        \dfrac{V}{R}
    \right]
    \ .
\end{equation}

@@

The procedure is as follows. Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$. They will need to be converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$. The adjusted size $\alpha_{\text{BH}}$ is
\begin{equation}
    \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
    k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
    \ .
\end{equation}
This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as positive results. For completeness, if $p_{(1)}>\alpha/n$, then $k=1$ and the Bonferroni correction is recovered. The procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}. However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.

@@

\begin{table}
    \input{../tables/inference_error_rate1.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, all standard Normal. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
\end{table}

\begin{table}
    \input{../tables/inference_error_rate2.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
\end{table}

>>>>

In this section, the single hypothesis test will be extended and the multiple hypothesis testing \citep{shaffer1995multiple, dudoit2003multiple} shall be reviewed.

@@

The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate. The FDR is the proportion of false positives out of all positive results, that is
\begin{equation}
    \expectation[\text{FDR}] = \expectation\left[
        \dfrac{V}{R}
    \right]
    \ .
\end{equation}
It is defined that $\text{FDR}=0$ when $R=0$.

@@

The procedure is as follows. Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$. They will need to be converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$. The adjusted size $\alpha_{\text{BH}}$ is
\begin{equation}
    \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
    k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
    \ .
\end{equation}
This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as positive results. For the case where $p_{(1)}>\alpha/n$, then $k=1$ shall be chosen so that the Bonferroni correction is used instead. The BH procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}. However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.

@@

\begin{table}
    \centering
    \input{../tables/inference_error_rate1.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, all standard Normal. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
\end{table}

\begin{table}
    \centering
    \input{../tables/inference_error_rate2.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
\end{table}
